---
title: "Charlottesville Police, Temporary Detentions"
output:
  rmdformats::material:
    logo: image/UVAEQUITYCENTER.jpeg
  
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(leaflet)
library(sf)
library(htmltools)
library(RColorBrewer)
library(rmdformats)

# I am demonstrating github


sf <- readRDS("data/sf_combined.Rds")


sflocations <- read_csv("data/sflocations.csv") %>% st_as_sf(
    coords = c("lon", "lat"),
    crs = 4326,
    remove = TRUE
  ) %>%
  filter(!Year %in% c(2019, 2020))

beats <- readRDS("data/beat_pop_map.Rds")

pal2 <- c("#52a2a9" ,"#d2a48b")


```


Introduction {data-orientation=rows}
=====================================
### About the Data {data-width=333}

A temporary detention involves a police officer holding and questioning an individual for a short amount of time. The police only need *reasonable suspicion* for a temporary detention. Detentions may be accompanied by some form of search or frisk, though not all detentions involve a search. Detentions can be dispatched in response to a call or initiated by an officer.

```{r Detentions by Race, echo = FALSE}
sf_summary_stats <- sf %>%
  group_by(race) %>%
  summarize(Totals = n()) %>%
  filter(race %in% c("B", "W"))

sf_summary_stats$race[sf_summary_stats$race == "B"] <- "Black"
sf_summary_stats$race[sf_summary_stats$race == "W"] <- "White"

sf_summary_stats <- sf_summary_stats%>%
  mutate(prop = Totals / sum(sf_summary_stats$Totals)) %>%
  mutate(ymax = cumsum(prop), ymin = c(0, head(ymax, n=-1)),
         labelPosition = (ymax + ymin) / 2, 
         label = Totals)

ggplot(sf_summary_stats, aes(x = race, y = Totals, fill = race)) +
  geom_bar(stat = "identity", width = 0.2) +
  scale_fill_hue(c = 40) +
  coord_flip() +
  scale_fill_manual(values = pal2) +
  geom_text(aes(y = Totals/1.2, label = label), size=7, color = "white") +
  geom_text(aes(y = -50, label = race), size=5, fontface=1) +
  ggtitle("Detentions by Charlottesville Police Officers from 2012-2017") +
  theme_void() +
  theme(legend.position = "none", 
      plot.title = element_text(size=15, face=4, hjust = .5))
```

```{r, echo=FALSE}
pop <- data.frame("race" = c("White", "Black", "Asian", "Multiracial", "Remaining"),
                  "value" = c(32565, 8782, 3370, 1443, 327)) %>%
  mutate(race = factor(race, levels = c("Black", "White", "Multiracial", "Asian", "Remaining")),
         group = "pop") %>%
  mutate(race = fct_collapse(race,
                             Remaining = c("Multiracial", "Asian", "Remaining")))%>%
  group_by(race) %>%
  summarize(value = sum(value)) %>%
  ungroup() %>% mutate(group = "pop") %>%
  filter(race %in% c("Black", "White")) %>%
  droplevels()

sf_race <- sf %>%
  filter(race %in% c("B", "W")) %>%
  mutate(race = factor(race),
         race = fct_recode(race,
                           Black = "B",
                           White = "W"),
         race = fct_relevel(race, "White"),
         type2 = factor(type),
         type2 = fct_recode(type2,
                            "Search/Frisk" = "STOP WITH SEARCH OR FRISK",
                            "No Search/Frisk" = "Search WITHOUT Stop-Frisk"))

sf_race_all <- sf_race %>%
  group_by(race) %>%
  summarize(value = n()) %>%
  ungroup() %>%
  mutate(group = "total")

sf_race_all <- rbind(sf_race_all, pop) %>%
  mutate(group = factor(group, levels = c("pop", "total")),
         race = fct_relevel(race, "White")) %>%
  arrange(group, desc(race)) %>%
  group_by(group) %>%
  mutate(label_pos = (cumsum(value) - value/2)/sum(value), 
         percent = paste0(round(value/sum(value)*100,1),"%")
         )

labellingdata <- data.frame(label = c("Population", "Detentions"), group = c("pop", "total"), pos = c(.90,.90) )



ggplot(sf_race_all, aes(x = group, y = value, fill = race)) +
  geom_bar(position="fill", stat="identity") +
  scale_fill_manual(values = pal2, name = "Race") +
  coord_polar("y", direction = 1) +
  scale_x_discrete(limits = c(" ", "pop","total")) +
  theme_void() +
  geom_text(data = filter(sf_race_all, race == "Black"), aes(x = group, y = label_pos, label = percent), size = 3, color = "white") +
  geom_text(data = labellingdata,
             aes(x = group, y = pos, label = label) ,inherit.aes = FALSE, size = 3, color = "white") 


```
This analysis is based on records of temporary detentions made by the City of Charlottesville Police. The data was received in response to Freedom of Information Act requests by Jeff Fogel made over multiple time periods. We have aggregated the data to two primary time periods: `r round(nrow(sf)/56,1)`

* Period 1: mid-July 2012 to mid-June 2014
* Period 2: January 2016 to mid-October 2016 combined with January 2017-December 2017

Navigate to additional pages for further analysis:

* **Who?** compares the percent of Black and White detentions to the overall population in the city.
* **Where?** visualizes where Black and White citizens are detained by the police.
* **Why?** shows the reason recorded by the police for the detention across Black and White residents.



Row
-----------------------------------------------------------------------

### Average Detentions per Month

```{r Detentions per Month, echo = FALSE}
avg <- round(nrow(sf)/56,1) #Enrique added 12 months to denominator
valueBox(avg, icon = "fa-hand-paper")
```

### Percent of Detentions with Search or Frisk
```{r Detentions with Search or Frisk, echo = FALSE}
frisk <- round(nrow(filter(sf, type == "STOP WITH SEARCH OR FRISK")) /
                 nrow(sf)*100, 0)
valueBox(frisk, icon = "fa-search")
```

### Ratio of Black to White Citizens Detained

```{r Black to White Citizens, echo = FALSE}



pal2 <- c("#8dd3c7" ,"#bebada")

ratio <- round(nrow(filter(sf_race, race == "Black")) / nrow(filter(sf_race, race == "White")),1)
valueBox(ratio, icon = "fa-user-friends")
```


Where? {data-orientation=rows}
===================================== 

### Where Do Police Detain People?

#### Map Details
* These maps display police detentions from both time periods, *2012-2014* and *2016-2017*. 
* Each point represents one individual stopped.
* Points *do not* represent the exact locations of each stop, but the density of the dots represents the density of detainments in a [geographic area](https://opendata.charlottesville.org/datasets/police-neighborhood-area).
* To help guide your eyes, detentions that include Search and Frisk are circled in red.
* Turn on and off underlying population characteristics through the box on the right
* Note that the underlying population percentages are based on a comparison of White and Black populations only to align with the races identifiable in the police data files.  

Row {data-height=700}
----------------------------------------------

### Detentions 2012 - 2014 & 2016 - 2017 

``` {r fig.width = 7, echo = FALSE }

l <-NULL

beats_data <- 
beats  %>% 
  mutate(`Percent White` = round(whitepopE/totalpopE*100,2),
         `Percent Black` = round(blackpopE/totalpopE*100,2)
        ) 

colorswhite <- colorRampPalette(brewer.pal(9, "Greens"))(9)[2:6]
whitepal <- colorBin(palette = colorswhite, domain = c(0,100), bins = 5)

colorsblack<- colorRampPalette(brewer.pal(9, "Purples"))(9)[2:6]
blackpal <- colorBin(palette = colorsblack, domain = c(0,100), bins = 5)

race.beats <- list(
      `Data Off` = beats_data %>% mutate(color = 0, df = "Data Off"),
     `Percent White` = beats_data %>% mutate(color = `Percent White`, df = "Percent White"),
     `Percent Black` = beats_data %>% mutate(color = `Percent Black`, df = "Percent Black")
     )

beatscolorfunction <- function(listname, color){
case_when(
     listname == names(race.beats)[2] ~   whitepal(color),
     listname == names(race.beats)[3] ~   blackpal(color),
     TRUE ~ "DCF0EF"
    )
}

beatsopacityfunction <- function(listname){
case_when(
     listname == names(race.beats)[2] ~   .5,
     listname == names(race.beats)[3] ~  .5,
     TRUE ~ 0.01
    )
}

l <- leaflet() %>%
  addProviderTiles("Stamen.Toner",
                   options = providerTileOptions(minZoom = 13))   %>%
  addMapPane("polygons", zIndex = 410) %>%
  addMapPane("circlemarkers", zIndex = 420) 


names(race.beats) %>%
   purrr::walk( function(df) {
    l <<- l %>%
           addPolygons(
              data = race.beats[[df]],
              weight = 3,
              fillOpacity = ~beatsopacityfunction(df),
              color = ~beatscolorfunction(df, color),
              group = df   ,
                            smoothFactor = 0.5,
              label = ~htmlEscape(paste0(NAME,  ifelse(color == 0, "", ifelse(df  == "Percent White", paste0(": ", color, "% White"), paste0(": ", color, "% Black") )  )))
              )
    })

## Add Race Dot Colors ## 

sflocationsmap <- 
  sflocations %>%
  mutate(RACE = ifelse(RACE == "W", "White", "Black"))
  
race.df <- split(sflocationsmap, sflocationsmap$RACE)
race.colors <- data.frame()

mycolors <- c("#6969B3", "#00AF98")
racelevels <- names(race.df)
racepal <- colorFactor(palette = mycolors,
                   domain = racelevels)

names(race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = race.df[[df]],
                color = ~racepal(df),
                weight = 0,
                radius = 2.5,
               fillOpacity = 1,
               group = df,
          label = ~htmlEscape(paste0("Offense: ", OFFENSE))

)
       
    })
  
sf.df <- split(sflocationsmap, sflocationsmap$SFTYPE)
sf.race.df   <- split(sf.df[["STOP WITH SEARCH OR FRISK"]], sf.df[["STOP WITH SEARCH OR FRISK"]]$RACE)

names(sf.race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = sf.race.df[[df]],
                color =  "red",
                weight = 1,
                radius = 6,
                fill = FALSE,
               group = df
       )
    })
    
html_legend <- "<svg width = '10' height = '10'> <circle cx='5' cy='5' r='5' stroke='red' fill = 'white' stroke-width = '1' /></svg> = Stop & Frisk"
               
l %>%
  addLayersControl(
    baseGroups =  names(race.beats),
    overlayGroups =  c(names(race.df)),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  htmlwidgets::onRender("
    function(el, x) {
      this.on('baselayerchange', function(e) {
        e.layer.bringToBack();
      })
    }") %>%
    addLegend("bottomleft", pal = racepal, values = names(race.df),
    title = "Race",
    opacity = 1
  ) %>%
    addControl(html = html_legend, position = "bottomright")



```

### Detentions by Beat
 
``` {r fig.height = 5, fig.width = 7, echo = FALSE}
 
sfs <- 
  sflocations %>%
  mutate(RACE = ifelse(RACE == "W", "White", "Black")) %>%
  as_tibble() %>% 
  select(BEAT_NO, RACE, OFFENSE, SFTYPE) %>%
  left_join(
  beats %>%
    as_tibble() %>%
    select(BEAT_NO, NAME) %>%
    mutate(BEAT_NO = as.numeric(BEAT_NO))
) %>%
  group_by(NAME, BEAT_NO, RACE, SFTYPE) %>%
  summarize(Counts = n()) %>%
    group_by(NAME) %>%
  mutate(total = sum(Counts)) %>%
  mutate(Counts = ifelse(RACE ==  "Black", Counts *-1, Counts)) %>%
  ungroup() %>%
  mutate(RACE = fct_relevel(RACE, "White")) %>%
  group_by(NAME, RACE) %>%
  mutate(RaceTot = sum(Counts)) %>%
  mutate(lab_pos = ifelse(RACE ==  "Black", RaceTot -2, RaceTot + 2))

pal2 <- c("#8dd3c7" ,"#bebada")

ggplot(sfs, aes(x = reorder(NAME, -total), fill = RACE, y = Counts, alpha = SFTYPE), color = "black") +
  geom_bar(stat = "identity") + labs(fill = "Race") +
  scale_fill_manual(values = pal2) +
  geom_text(data = sfs %>% select(NAME, lab_pos, RaceTot) %>% unique(), aes(x = NAME, y = lab_pos, label = abs(RaceTot)), size = 3, inherit.aes = FALSE) +
  coord_flip() +
  scale_y_continuous(labels = function(x){abs(x)}, limits = c(-60, 60), breaks = c(seq(-40, 40, 20), 0)) +
  scale_alpha_discrete(range = c(.6, 1)) +
  annotate("text", x = 29, y = -15, label = "Black" ) +
    annotate("text", x = 29, y = 15, label = "White" ) +
   annotate("rect", xmin = 25, xmax = 26, ymin = 10, ymax = 14, alpha = 1, fill = "#8dd3c7") +
   annotate("text", x = 25.5, y = 15, label = "= With Stop and Frisk", size = 3, hjust = 0)+
    annotate("rect", xmin = 23.5, xmax = 24.5, ymin = 10, ymax = 14, alpha = .6, fill = "#8dd3c7") +
   annotate("text", x = 24, y = 15, label = "= Without Stop and Frisk", size = 3, hjust = 0)+
  geom_hline(yintercept  = 0) +
  theme_minimal() +
  theme(
    legend.position = "none",
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.title = element_blank(),
    panel.grid.major.y = element_line(linetype = "dashed"),
 #   axis.text.x = element_blank(),
 axis.line.x = element_line(),
 axis.ticks.x = element_line()

  ) 


```

Row 
----------------------------------------------
### Changes Over Time 
Trends:

* Greater dispersion of stop and frisk throughout the city during the 2017
* Noticeable *decrease* of stop and frisk in the Rose Hill nieghborhood.
* Stop and frisk of black individuals in areas with predominantly student housing *increased*, specifically in the Grady, Rugby Road, and Emmet Street Areas in addition to the areas south of west main by the train tracks and Jefferson Park Avenue.
* Stop and Frisk *increased significantly*, particularly for black individuals, in the Prospect/Orangedale Ave area. 


Row 
----------------------------------------------

### 2012-2014 
``` {r , echo = FALSE}

l <-NULL

beats_data <- 
beats  %>% 
  mutate(`Percent White` = round(whitepopE/totalpopE*100,2),
         `Percent Black` = round(blackpopE/totalpopE*100,2)
        ) 

colorswhite <- colorRampPalette(brewer.pal(9, "Greens"))(9)[2:6]
whitepal <- colorBin(palette = colorswhite, domain = c(0,100), bins = 5)

colorsblack<- colorRampPalette(brewer.pal(9, "Purples"))(9)[2:6]
blackpal <- colorBin(palette = colorsblack, domain = c(0,100), bins = 5)

race.beats <- list(
      `Data Off` = beats_data %>% mutate(color = 0, df = "Data Off"),
     `Percent White` = beats_data %>% mutate(color = `Percent White`, df = "Percent White"),
     `Percent Black` = beats_data %>% mutate(color = `Percent Black`, df = "Percent Black")
     )

beatscolorfunction <- function(listname, color){
case_when(
     listname == names(race.beats)[2] ~   whitepal(color),
     listname == names(race.beats)[3] ~   blackpal(color),
     TRUE ~ "DCF0EF"
    )
}

beatsopacityfunction <- function(listname){
case_when(
     listname == names(race.beats)[2] ~   .5,
     listname == names(race.beats)[3] ~  .5,
     TRUE ~ .01
    )
}


l <- leaflet() %>%
  addProviderTiles("Stamen.Toner",
                   options = providerTileOptions(minZoom = 13))   %>%
  addMapPane("polygons", zIndex = 410) %>%
  addMapPane("circlemarkers", zIndex = 420) 

names(race.beats) %>%
   purrr::walk( function(df) {
    l <<- l %>%
           addPolygons(
              data = race.beats[[df]],
              weight = 3,
              fillOpacity = ~beatsopacityfunction(df),
              color = ~beatscolorfunction(df, color),
              group = df   ,
              smoothFactor = 0.5,
              label = ~htmlEscape(paste0(NAME,  ifelse(color == 0, "", ifelse(df  == "Percent White", paste0(": ", color, "% White"), paste0(": ", color, "% Black") )  )))

              )
    })

## Add Race Dot Colors ## 

sflocationsmap <- 
  sflocations %>%
  mutate(RACE = ifelse(RACE == "W", "White", "Black")) %>%
  filter(Year < 2015) %>%
    mutate(labels =  paste0( '<p> Race:', RACE, '<p></p>', 
         SFTYPE, '</p><p> Offense:', 
          OFFENSE, '</p>' ) 
)
  
race.df <- split(sflocationsmap, sflocationsmap$RACE)
race.colors <- data.frame()

mycolors <- c("#6969B3", "#00AF98")
racelevels <- names(race.df)
racepal <- colorFactor(palette = mycolors,
                   domain = racelevels)

names(race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = race.df[[df]],
                color = ~racepal(df),
                weight = 0,
                radius = 2.5,
               fillOpacity = 1,
               group = df,
               label = ~htmlEscape(paste0("Offense: ", OFFENSE))

       )
    })
  
sf.df <- split(sflocationsmap, sflocationsmap$SFTYPE)
sf.race.df   <- split(sf.df[["STOP WITH SEARCH OR FRISK"]], sf.df[["STOP WITH SEARCH OR FRISK"]]$RACE)

names(sf.race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = sf.race.df[[df]],
                color =  "red",
                weight = 1,
                radius = 6,
                fill = FALSE,
               group = df
       )
    })
    
               
l %>%
  addLayersControl(
    baseGroups =  names(race.beats),
    overlayGroups =  c(names(race.df)),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  htmlwidgets::onRender("
    function(el, x) {
      this.on('baselayerchange', function(e) {
        e.layer.bringToBack();
      })
    }") %>%
    addLegend("bottomleft", pal = racepal, values = names(race.df),
    title = "Race",
    opacity = 1
  ) %>%
    addControl(html = html_legend, position = "bottomright")


```

### 2016-2017
``` {r, echo = FALSE }

l <-NULL

beats_data <- 
beats  %>% 
  mutate(`Percent White` = round(whitepopE/totalpopE*100,2),
         `Percent Black` = round(blackpopE/totalpopE*100,2)
        ) 

colorswhite <- colorRampPalette(brewer.pal(9, "Greens"))(9)[2:6]
whitepal <- colorBin(palette = colorswhite, domain = c(0,100), bins = 5)

colorsblack<- colorRampPalette(brewer.pal(9, "Purples"))(9)[2:6]
blackpal <- colorBin(palette = colorsblack, domain = c(0,100), bins = 5)

race.beats <- list(
      `Data Off` = beats_data %>% mutate(color = 0, df = "Data Off"),
     `Percent White` = beats_data %>% mutate(color = `Percent White`, df = "Percent White"),
     `Percent Black` = beats_data %>% mutate(color = `Percent Black`, df = "Percent Black")
     )

beatscolorfunction <- function(listname, color){
case_when(
     listname == names(race.beats)[2] ~   whitepal(color),
     listname == names(race.beats)[3] ~   blackpal(color),
     TRUE ~ "DCF0EF"
    )
}

beatsopacityfunction <- function(listname){
case_when(
     listname == names(race.beats)[2] ~   .5,
     listname == names(race.beats)[3] ~  .5,
     TRUE ~ 0
    )
}


l <- leaflet() %>%
  addProviderTiles("Stamen.Toner",
                   options = providerTileOptions(minZoom = 13))   %>%
  addMapPane("polygons", zIndex = 410) %>%
  addMapPane("circlemarkers", zIndex = 420) 

names(race.beats) %>%
   purrr::walk( function(df) {
    l <<- l %>%
           addPolygons(
              data = race.beats[[df]],
              weight = 3,
              fillOpacity = ~beatsopacityfunction(df),
              color = ~beatscolorfunction(df, color),
              group = df   ,
             smoothFactor = 0.5,
              label = ~htmlEscape(paste0(NAME,  ifelse(color == 0, "", ifelse(df  == "Percent White", paste0(": ", color, "% White"), paste0(": ", color, "% Black") )  )))
              )
    })

## Add Race Dot Colors ## 

sflocationsmap <- 
  sflocations %>%
  mutate(RACE = ifelse(RACE == "W", "White", "Black")) %>%
  filter(Year > 2015) %>% ##################################################### YEAR 
   mutate(labels =  paste0( '<p> Race:', RACE, '<p></p>', 
         SFTYPE, '</p><p> Offense:', 
          OFFENSE, '</p>' ) 
)
  
race.df <- split(sflocationsmap, sflocationsmap$RACE)
race.colors <- data.frame()

mycolors <- c("#6969B3", "#00AF98")
racelevels <- names(race.df)
racepal <- colorFactor(palette = mycolors,
                   domain = racelevels)

names(race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = race.df[[df]],
                fillColor = ~racepal(df),
                weight = 0,
                radius = 2.5,
               fillOpacity = 1,
               group = df,
              label = ~htmlEscape(paste0("Offense: ", OFFENSE))

       )
    }) 
  
sf.df <- split(sflocationsmap, sflocationsmap$SFTYPE)
sf.race.df   <- split(sf.df[["STOP WITH SEARCH OR FRISK"]], sf.df[["STOP WITH SEARCH OR FRISK"]]$RACE)

names(sf.race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = sf.race.df[[df]],
                color =  "red",
                weight = 1,
                radius = 6,
                fill = FALSE,
               group = df
       )
    })
    
               
l %>%
  addLayersControl(
    baseGroups =  names(race.beats),
    overlayGroups =  c(names(race.df)),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  htmlwidgets::onRender("
    function(el, x) {
      this.on('baselayerchange', function(e) {
        e.layer.bringToBack();
      })
    }")  %>%
    addLegend("bottomleft", pal = racepal, values = names(race.df),
    title = "Race",
    opacity = 1
  ) %>%
    addControl(html = html_legend, position = "bottomright")


```

Row 
----------------------------------------------
### Over Policing & Exclusive Spaces

The data does not record why police enter certain spaces, whether it is an officer-initiated discretionary stop or a response to a call.  We also do not have data on whether or not a detainment led to an arrest. The offense listed is the reason the police officer recorded to justify the stop based on reasonable suspicion, not a determination that the offense occured. Beacuse of this, it is difficult to say that police detainments are an indicator of crime. Fewer detainments does not immediatley signify less crime in an area, just less police activity. 

Below, we highlight three areas, a predominantly black residential space, a predominantly white residential space, and a public walking mall to investigate who police detain and where.

Row {data-height=600}
----------------------------------------------
### Ridge Street & Prospect-Orangedale Neighborhoods {data-height=600}


``` {r, echo = FALSE}
l <- NULL

beats_data <- 
beats  %>% 
  mutate(`Percent White` = round(whitepopE/totalpopE*100,2),
         `Percent Black` = round(blackpopE/totalpopE*100,2)
        ) 

beatsopacityfunction <- function(BEAT_NO){
case_when(
     BEAT_NO %in% c("12", "21" )  ~ 0,
     TRUE ~ .9
    )
}


l <- leaflet(options = leafletOptions(zoomControl = FALSE)) %>%
  addProviderTiles("Stamen.Toner",
                   options = providerTileOptions(minZoom = 15, maxZoom = 16))   %>%
         setView( lng =  -78.48875, lat = 38.02272 , zoom = 15) %>%

  addMapPane("polygons", zIndex = 410) %>%
  addMapPane("circlemarkers", zIndex = 420) %>%
    # setMaxBounds( lng1 = -87.94011
    #              , lat1 = 41.64454
    #              , lng2 = -87.52414
    #              , lat2 = 42.02304 ) %>%
           addPolygons(
              data = beats_data,
              weight = 10,
              fillOpacity = ~beatsopacityfunction(BEAT_NO),
              color = "grey",
               smoothFactor = 0.5,

              )

## Add Race Dot Colors ## 
sflocationsmap <- 
  sflocations %>%
  mutate(RACE = ifelse(RACE == "W", "White", "Black")) %>%
  filter(BEAT_NO  %in%  c(12, 21 )) 
  
race.df <- split(sflocationsmap, sflocationsmap$RACE)
race.colors <- data.frame()

mycolors <- c("#6969B3", "#00AF98")
racelevels <- names(race.df)
racepal <- colorFactor(palette = mycolors,
                   domain = racelevels)

names(race.df) %>%
   purrr::walk(  function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = race.df[[df]],
                color = ~racepal(df),
                weight = 0,
                radius = 4,
               fillOpacity = 1,
               group = df,
              label = ~htmlEscape(paste0("Offense: ", OFFENSE))
)
    })
  
sf.df <- split(sflocationsmap, sflocationsmap$SFTYPE)
sf.race.df   <- split(sf.df[["STOP WITH SEARCH OR FRISK"]], sf.df[["STOP WITH SEARCH OR FRISK"]]$RACE)

names(sf.race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = sf.race.df[[df]],
                color =  "red",
                weight = 1,
                radius = 7,
                fill = FALSE,
               group = df
       )
    }) 
               
l %>%
    addLegend("bottomleft", pal = racepal, values = names(race.df),
    title = "Race",
    opacity = 1
  ) %>%
    addControl(html = html_legend, position = "bottomright")


```


### Martha Jefferson & Locust Grove Neighborhoods {data-height=600}

``` {r, echo = FALSE}
l <- NULL

beats_data <- 
beats  %>% 
  mutate(`Percent White` = round(whitepopE/totalpopE*100,2),
         `Percent Black` = round(blackpopE/totalpopE*100,2)
        ) 

beatsopacityfunction <- function(BEAT_NO){
case_when(
     BEAT_NO %in% c("08", "19" )  ~ 0,
     TRUE ~ .9
    )
}


l <- leaflet(options = leafletOptions(zoomControl = FALSE)) %>%
  addProviderTiles("Stamen.Toner",
                   options = providerTileOptions(minZoom = 15, maxZoom = 16))   %>%
         setView( lng = -78.46738, lat = 38.03754 , zoom = 15) %>%

  addMapPane("polygons", zIndex = 410) %>%
  addMapPane("circlemarkers", zIndex = 420) %>%
    # setMaxBounds( lng1 = -87.94011
    #              , lat1 = 41.64454
    #              , lng2 = -87.52414
    #              , lat2 = 42.02304 ) %>%
           addPolygons(
              data = beats_data,
              weight = 10,
              fillOpacity = ~beatsopacityfunction(BEAT_NO),
              color = "grey",
               smoothFactor = 0.5,

              )

## Add Race Dot Colors ## 
sflocationsmap <- 
  sflocations %>%
  mutate(RACE = ifelse(RACE == "W", "White", "Black")) %>%
  filter(BEAT_NO  %in%  c(8, 19)) 
  
race.df <- split(sflocationsmap, sflocationsmap$RACE)
race.colors <- data.frame()

mycolors <- c("#6969B3", "#00AF98")
racelevels <- names(race.df)
racepal <- colorFactor(palette = mycolors,
                   domain = racelevels)

names(race.df) %>%
   purrr::walk(  function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = race.df[[df]],
                color = ~racepal(df),
                weight = 0,
                radius = 4,
               fillOpacity = 1,
               group = df,
              label = ~htmlEscape(paste0("Offense: ", OFFENSE))
)
    })
  
sf.df <- split(sflocationsmap, sflocationsmap$SFTYPE)
sf.race.df   <- split(sf.df[["STOP WITH SEARCH OR FRISK"]], sf.df[["STOP WITH SEARCH OR FRISK"]]$RACE)

names(sf.race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = sf.race.df[[df]],
                color =  "red",
                weight = 1,
                radius = 7,
                fill = FALSE,
               group = df
       )
    }) 
               
l %>%
    addLegend("bottomleft", pal = racepal, values = names(race.df),
    title = "Race",
    opacity = 1
  ) %>%
    addControl(html = html_legend, position = "bottomright")


```

Row {data-height=600}
----------------------------------------------

### Downtown {data-width=600}
``` {r, echo = FALSE}
l <- NULL

beats_data <- 
beats  %>% 
  mutate(`Percent White` = round(whitepopE/totalpopE*100,2),
         `Percent Black` = round(blackpopE/totalpopE*100,2)
        ) 

beatsopacityfunction <- function(BEAT_NO){
case_when(
     BEAT_NO == "01"  ~   0,
     TRUE ~ .9
    )
}

l <- leaflet(options = leafletOptions(zoomControl = FALSE)) %>%
  addProviderTiles("Stamen.Toner",
                   options = providerTileOptions(minZoom = 16, maxZoom = 17))   %>%
         setView( lng = -78.4795, lat = 38.0305, zoom = 16) %>%

  addMapPane("polygons", zIndex = 410) %>%
  addMapPane("circlemarkers", zIndex = 420) %>%
    # setMaxBounds( lng1 = -87.94011
    #              , lat1 = 41.64454
    #              , lng2 = -87.52414
    #              , lat2 = 42.02304 ) %>%
           addPolygons(
              data = beats_data,
              weight = 3,
              fillOpacity = ~beatsopacityfunction(BEAT_NO),
              color = "grey",
               smoothFactor = 0.5,

              )

## Add Race Dot Colors ## 
sflocationsmap <- 
  sflocations %>%
  mutate(RACE = ifelse(RACE == "W", "White", "Black")) %>%
  filter(BEAT_NO == 1) %>%
    mutate(labels =  paste0( '<p> Race:', RACE, '<p></p>', 
         SFTYPE, '</p><p> Offense:', 
          OFFENSE, '</p>' ) 
)
  
race.df <- split(sflocationsmap, sflocationsmap$RACE)
race.colors <- data.frame()

mycolors <- c("#6969B3", "#00AF98")
racelevels <- names(race.df)
racepal <- colorFactor(palette = mycolors,
                   domain = racelevels)

names(race.df) %>%
   purrr::walk(  function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = race.df[[df]],
                color = ~racepal(df),
                weight = 0,
                radius = 4,
               fillOpacity = 1,
               group = df,
              label = ~htmlEscape(paste0("Offense: ", OFFENSE))
)
    })
  
sf.df <- split(sflocationsmap, sflocationsmap$SFTYPE)
sf.race.df   <- split(sf.df[["STOP WITH SEARCH OR FRISK"]], sf.df[["STOP WITH SEARCH OR FRISK"]]$RACE)

names(sf.race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = sf.race.df[[df]],
                color =  "red",
                weight = 1,
                radius = 7,
                fill = FALSE,
               group = df
       )
    }) 
               
l %>%
    addLegend("bottomleft", pal = racepal, values = names(race.df),
    title = "Race",
    opacity = 1
  ) %>%
    addControl(html = html_legend, position = "bottomright")

sfs %>% filter(BEAT_NO %in% c("8", "19", "21", "12"))

```


### Analysis

Historically, racial covenants prohibited Black individuals from living in the Martha Jefferson and Locust Grove. That legacy continues today

* An estimated 1401 White individuals live in the Martha Jefferson and Locust Grove Neighborhoods
* 3 (2.14 for every 1000) White individuals were detained in the Martha Jefferson and Locust Grove Neighborhoods
* An estimated 1731	Black individuals live in in Prospect Orangedale Ave and Ridge St Neighborhoods
* 68 (39 for every 1000) Black individuals were detained in the Prospect Orangedale Ave and Ridge St Neighborhoods

The Downtown Mall is a public space for free use by Charlottesville residents. 

* In the periods of 2012 -2014 and 2016-2017, 26 Black individuals were detained by police 
* 22 White individuals were detained in the same period. 
* 73% of Black individuals stopped (19 individuals) were also searched and frisked 
* 31% (7) of White individuals were also searched and frisked. 




