---
title: "Charlottesville Police, Temporary Detentions"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(leaflet)
library(sf)
library(htmltools)
library(RColorBrewer)

sf <- readRDS("data/sf_combined.Rds")


sflocations <- read_csv("data/finaldata/sflocations.csv") %>% st_as_sf(
    coords = c("lon", "lat"),
    crs = 4326,
    remove = TRUE
  ) %>%
  filter(!Year %in% c(2019, 2020))

beats <- readRDS("beat_pop_map.Rds")


```

Introduction {data-orientation=rows}
=====================================

Row
-----------------------------------------------------------------------

### Average Detentions per Month

```{r}
avg <- round(nrow(sf)/44,1)
valueBox(avg, icon = "fa-hand-paper")
```

### Percent of Detentions with Search or Frisk
```{r}
frisk <- round(nrow(filter(sf, type == "STOP WITH SEARCH OR FRISK")) /
                 nrow(sf)*100, 0)
valueBox(frisk, icon = "fa-search")
```

### Ratio of Black to White Citizens Detained

```{r}
sf_race <- sf %>%
  filter(race %in% c("B", "W")) %>%
  mutate(race = factor(race),
         race = fct_recode(race,
                           Black = "B",
                           White = "W"),
         race = fct_relevel(race, "White"),
         type2 = factor(type),
         type2 = fct_recode(type2,
                            "Search/Frisk" = "STOP WITH SEARCH OR FRISK",
                            "No Search/Frisk" = "Search WITHOUT Stop-Frisk"))


pal2 <- c("#8dd3c7" ,"#bebada")

ratio <- round(nrow(filter(sf_race, race == "Black")) / nrow(filter(sf_race, race == "White")),1)
valueBox(ratio, icon = "fa-user-friends")
```

Row
-----------------------------------------------------------------------

### About the Data {data-width=333}

A temporary detention involves a police officer holding and questioning an individual for a short amount of time. The police only need *reasonable suspicion* for a detention. Detentions may be accompanied by some form of search or frisk, though not all detentions will involve a search. Detentions can be initiated by an officer or dispatched in response to a call.

This analysis is based on records of temporary detentions made by the City of Charlottesville Police. The data was received in response to Freedom of Information Act requests (by -- attribution for requesting?) made over multiple time periods. We have aggregated the data to two primary time periods:

* Period 1: mid-July 2012 to mid-June 2014
* Period 2: January 2016 to mid-October 2016 combined with January 2017-December 2017

Navigate to additional pages for further analysis:

* **Composition** compares the percent of Black and White detentions to the overall population in the city.
* **Mapping** visualizes where Black and White citizens are detained by the police.
* **Offenses** shows the nature of the offense reported as the reason for the detention across Black and White residents.

### Detentions, with and without Search/Frisk, by Race

```{r}
# for annotation
tots <- sf_race %>% group_by(period, type2) %>% summarize(tots = n())
racetots <- sf_race %>% group_by(period, type2, race) %>% summarize(racetot = n())
racetots <- racetots %>% left_join(tots)
racetots <- racetots %>% mutate(percent = round((racetot/tots)*100,0),
                                percent_lab = paste0(percent, "%"),
                                race = fct_relevel(race, "White")) %>%
  group_by(period, type2) %>%
  arrange(period, type2, race) %>%
  mutate(lab_height =  racetot/2)


ggplot(sf_race, aes(x = type2, fill = race)) +
  geom_bar(position = "dodge") + facet_wrap(~period) +
  scale_fill_manual(values = pal2) +
  labs(fill = "Race") +
  theme(axis.title = element_blank()) +
  geom_text(data = arrange(racetots, race), aes(x = type2, y = lab_height, fill = race, label = percent_lab), position = position_dodge(width = 1)) +
 geom_text(data = arrange(racetots, race), aes(x = type2, y = racetot + 5, fill = race, label = racetot), position = position_dodge(width = 1))

```



Composition {data-orientation=rows}
=====================================

Row
-----------------------------------------------------------------------

### Detentions per 1000 population for Black residents (2-year period)
```{r}
bl_pc <- round(((nrow(filter(sf_race, race == "Black"))/2) / 8782)*1000,1)
valueBox(bl_pc, icon = "fa-users")
```

### Detentions per 1000 population for White residents (2-year period)
```{r}
wh_pc <- round(((nrow(filter(sf_race, race == "White"))/2) / 32565)*1000,1)
valueBox(wh_pc, icon = "fa-user")
```


Row {.tabset}
-----------------------------------------------------------------------

```{r}
pop <- data.frame("race" = c("White", "Black", "Asian", "Multiracial", "Remaining"),
                  "value" = c(32565, 8782, 3370, 1443, 327))

pop <- pop %>%
  mutate(race = factor(race, levels = c("Black", "White", "Multiracial", "Asian", "Remaining")),
         group = "pop")

pop3 <- pop %>%
  mutate(race = fct_collapse(race,
                             Remainig = c("Multiracial", "Asian", "Remaining"))) %>%
  group_by(race) %>%
  summarize(value = sum(value)) %>%
  ungroup() %>% mutate(group = "pop")

pop2 <- pop3 %>%
  filter(race %in% c("Black", "White")) %>%
  droplevels()
```

### Detentions Relative to Population

```{r}
# total by race
sf_race_all <- sf_race %>%
  group_by(race) %>%
  summarize(value = n()) %>%
  ungroup() %>%
  mutate(group = "total")

sf_race_all <- rbind(sf_race_all, pop2) %>%
  mutate(group = factor(group, levels = c("pop", "total")),
         race = fct_relevel(race, "White")) %>%
  arrange(group, desc(race)) %>%
  group_by(group) %>%
  mutate(label_pos = (cumsum(value) - value/2)/sum(value), 
         percent = paste0(round(value/sum(value)*100,1),"%")
         )

labellingdata <- data.frame(label = c("Population", "Detentions"), group = c("pop", "total"), pos = c(.90,.90) )


ggplot(sf_race_all, aes(x = group, y = value, fill = race)) +
  geom_bar(position="fill", stat="identity") +
  scale_fill_manual(values = pal2) +
  coord_polar("y", direction = 1) +
  scale_x_discrete(limits = c(" ", "pop","total")) +
  theme_void() +
  geom_text(  data = filter(sf_race_all, race == "Black"), aes(x = group, y = label_pos, label = percent), size = 3) +
  geom_text( data = labellingdata,
             aes(x = group, y = pos, label = label) ,inherit.aes = FALSE, size = 3) 

```

### By Time Period

```{r}
sf_race_period <- sf_race %>%
  group_by(period, race) %>%
  summarize(value = n()) %>%
  ungroup() %>%
  mutate(group = "period")

pop2_p1 <- pop2 %>%
  mutate(period = "2012-2014")
pop2_p2 <- pop2 %>%
  mutate(period = "2016-2017")

sf_race_period <- rbind(sf_race_period, pop2_p1, pop2_p2) %>%
  mutate(group = factor(group, levels = c("pop", "period")),
         race = fct_relevel(race, "White")) %>%
  arrange(group, period, desc(race)) %>%
  group_by(group, period) %>%
  mutate(label_pos = (cumsum(value) - value/2)/sum(value), 
         percent = paste0(round(value/sum(value)*100,1),"%")
         )

labellingdata <- data.frame(label = rep(c("Population", "Detentions"),2), group = rep(c("pop", "period"),2), pos = rep(c(.90,.90),2), period = rep(c("2012-2014", "2016-2017"), each = 2 ))


ggplot(sf_race_period, aes(x = group, y = value, fill = race)) +
  geom_bar(position="fill", stat = "identity") +
  scale_fill_manual(values = pal2) +
  coord_polar("y", direction = 1) +
  scale_x_discrete(limits = c(" ", "pop","period")) +
  theme_void() +
  geom_text(  data = filter(sf_race_period, race == "Black"), aes(x = group, y = label_pos, label = percent), size = 3) +
    geom_text( data = labellingdata,
             aes(x = group, y = pos, label = label) ,inherit.aes = FALSE, size = 3) +
  facet_wrap(~period)
```

### By Stop and Frisk

```{r}
sf_race_type <- sf_race %>%
  group_by(type2, race) %>%
  summarize(value = n()) %>%
  ungroup() %>%
  mutate(group = "type") %>%
  rename(type = type2)

pop2_t1 <- pop2 %>%
  mutate(type = "No Search/Frisk")
pop2_t2 <- pop2 %>%
  mutate(type = "Search/Frisk")

sf_race_type <- rbind(sf_race_type, pop2_t1, pop2_t2) %>%
  mutate(group = factor(group, levels = c("pop", "type")),
         race = fct_relevel(race, "White")) %>%
  arrange(group, type, desc(race)) %>%
  group_by(group, type) %>%
  mutate(label_pos = (cumsum(value) - value/2)/sum(value), 
         percent = paste0(round(value/sum(value)*100,1),"%")) 

labellingdata <- data.frame(label = rep(c("Population", "Detentions"),2), group = rep(c("pop", "type"),2), pos = rep(c(.90,.90),2), type = rep(c("No Search/Frisk", "Search/Frisk"), each = 2 ))

ggplot(sf_race_type, aes(x = group, y = value, fill = race)) +
  geom_bar(position="fill", stat = "identity") +
  scale_fill_manual(values = pal2) +
  coord_polar("y", direction = 1) +
  scale_x_discrete(limits = c(" ", "pop","type")) +
  geom_text(  data = filter(sf_race_type, race == "Black"), aes(x = group, y = label_pos, label = percent), size = 3) +
    geom_text( data = labellingdata,
             aes(x = group, y = pos, label = label) ,inherit.aes = FALSE, size = 3) +
  theme_void() +
  facet_wrap(~type) 
```




Mapping {data-orientation=rows}
===================================== 

### Who do Police Detain and Where?

* These maps display all police detainments between 2012-2014 and 2016-2017. 
* Points do not represent exact locations of each stop, rather the density of the dots represent the density of detainments in a geographic area. 
* To help guide your eyes, detainments that include Search and Frisk are circled in red 
* Turn on and off underlying population characteristics through the box on the right to see how who primariliy occupies a specific district relates to who is detained in that space.


Row {data-height=800}
----------------------------------------------

### All Years of Data 

``` {r fig.width = 7 }

l <-NULL

beats_data <- 
beats  %>% 
  mutate(`Percent White` = round(whitepopE/totalpopE*100,2),
         `Percent Black` = round(blackpopE/totalpopE*100,2)
        ) 

colorswhite <- colorRampPalette(brewer.pal(9, "Greens"))(9)[2:6]
whitepal <- colorBin(palette = colorswhite, domain = c(0,100), bins = 5)

colorsblack<- colorRampPalette(brewer.pal(9, "Purples"))(9)[2:6]
blackpal <- colorBin(palette = colorsblack, domain = c(0,100), bins = 5)

race.beats <- list(
      `Data Off` = beats_data %>% mutate(color = 0, df = "Data Off"),
     `Percent White` = beats_data %>% mutate(color = `Percent White`, df = "Percent White"),
     `Percent Black` = beats_data %>% mutate(color = `Percent Black`, df = "Percent Black")
     )

beatscolorfunction <- function(listname, color){
case_when(
     listname == names(race.beats)[2] ~   whitepal(color),
     listname == names(race.beats)[3] ~   blackpal(color),
     TRUE ~ "DCF0EF"
    )
}

beatsopacityfunction <- function(listname){
case_when(
     listname == names(race.beats)[2] ~   .5,
     listname == names(race.beats)[3] ~  .5,
     TRUE ~ 0.01
    )
}

l <- leaflet() %>%
  addProviderTiles("Stamen.Toner",
                   options = providerTileOptions(minZoom = 13))   %>%
  addMapPane("polygons", zIndex = 410) %>%
  addMapPane("circlemarkers", zIndex = 420) 


names(race.beats) %>%
   purrr::walk( function(df) {
    l <<- l %>%
           addPolygons(
              data = race.beats[[df]],
              weight = 3,
              fillOpacity = ~beatsopacityfunction(df),
              color = ~beatscolorfunction(df, color),
              group = df   ,
                            smoothFactor = 0.5,
              label = ~htmlEscape(NAME)

              )
    })

## Add Race Dot Colors ## 

sflocationsmap <- 
  sflocations %>%
  mutate(RACE = ifelse(RACE == "W", "White", "Black"))
  
race.df <- split(sflocationsmap, sflocationsmap$RACE)
race.colors <- data.frame()

mycolors <- c("#6969B3", "#00AF98")
racelevels <- names(race.df)
racepal <- colorFactor(palette = mycolors,
                   domain = racelevels)

names(race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = race.df[[df]],
                color = ~racepal(df),
                weight = 0,
                radius = 2.5,
               fillOpacity = 1,
               group = df
)
       
    })
  
sf.df <- split(sflocationsmap, sflocationsmap$SFTYPE)
sf.race.df   <- split(sf.df[["STOP WITH SEARCH OR FRISK"]], sf.df[["STOP WITH SEARCH OR FRISK"]]$RACE)

names(sf.race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = sf.race.df[[df]],
                color =  "red",
                weight = 1,
                radius = 6,
                fill = FALSE,
               group = df
       )
    })
    
               
l %>%
  addLayersControl(
    baseGroups =  names(race.beats),
    overlayGroups =  c(names(race.df)),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  htmlwidgets::onRender("
    function(el, x) {
      this.on('baselayerchange', function(e) {
        e.layer.bringToBack();
      })
    }") %>%
    addLegend("bottomleft", pal = racepal, values = names(race.df),
    title = "Race",
    opacity = 1
  )


```


Row 
----------------------------------------------
### Changes Over Time 
Segmenting by time period, we see a few trends

* Firstly, there is greater dispersion of stop and frisk throughout the city during the 2017 time period
* That said, there is a noticeable decrease of stop and frisk in some predominantly black neighborhoods such as the Rose Hill nieghborhood.
* Despite those decreases, stop and frisk of black individuals in areas with predominantly student housing increased, specifically in the Grady, Rugby Road, and Emmet Street Areas in addition to the areas south of west main by the train tracks and Jefferson Park Avenue.
* Finally, Stop and Frisk increased significantly, particularly for black individuals, in the Prospect/Orangedale Ave area. 


Row 
----------------------------------------------

### 2012-2014 
``` {r }

l <-NULL

beats_data <- 
beats  %>% 
  mutate(`Percent White` = round(whitepopE/totalpopE*100,2),
         `Percent Black` = round(blackpopE/totalpopE*100,2)
        ) 

colorswhite <- colorRampPalette(brewer.pal(9, "Greens"))(9)[2:6]
whitepal <- colorBin(palette = colorswhite, domain = c(0,100), bins = 5)

colorsblack<- colorRampPalette(brewer.pal(9, "Purples"))(9)[2:6]
blackpal <- colorBin(palette = colorsblack, domain = c(0,100), bins = 5)

race.beats <- list(
      `Data Off` = beats_data %>% mutate(color = 0, df = "Data Off"),
     `Percent White` = beats_data %>% mutate(color = `Percent White`, df = "Percent White"),
     `Percent Black` = beats_data %>% mutate(color = `Percent Black`, df = "Percent Black")
     )

beatscolorfunction <- function(listname, color){
case_when(
     listname == names(race.beats)[2] ~   whitepal(color),
     listname == names(race.beats)[3] ~   blackpal(color),
     TRUE ~ "DCF0EF"
    )
}

beatsopacityfunction <- function(listname){
case_when(
     listname == names(race.beats)[2] ~   .5,
     listname == names(race.beats)[3] ~  .5,
     TRUE ~ .01
    )
}


l <- leaflet() %>%
  addProviderTiles("Stamen.Toner",
                   options = providerTileOptions(minZoom = 13))   %>%
  addMapPane("polygons", zIndex = 410) %>%
  addMapPane("circlemarkers", zIndex = 420) 

names(race.beats) %>%
   purrr::walk( function(df) {
    l <<- l %>%
           addPolygons(
              data = race.beats[[df]],
              weight = 3,
              fillOpacity = ~beatsopacityfunction(df),
              color = ~beatscolorfunction(df, color),
              group = df   ,
              smoothFactor = 0.5,
              label = ~htmlEscape(NAME)

              )
    })

## Add Race Dot Colors ## 

sflocationsmap <- 
  sflocations %>%
  mutate(RACE = ifelse(RACE == "W", "White", "Black")) %>%
  filter(Year < 2015) %>%
    mutate(labels =  paste0( '<p> Race:', RACE, '<p></p>', 
         SFTYPE, '</p><p> Offense:', 
          OFFENSE, '</p>' ) 
)
  
race.df <- split(sflocationsmap, sflocationsmap$RACE)
race.colors <- data.frame()

mycolors <- c("#6969B3", "#00AF98")
racelevels <- names(race.df)
racepal <- colorFactor(palette = mycolors,
                   domain = racelevels)

names(race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = race.df[[df]],
                color = ~racepal(df),
                weight = 0,
                radius = 2.5,
               fillOpacity = 1,
               group = df
       )
    })
  
sf.df <- split(sflocationsmap, sflocationsmap$SFTYPE)
sf.race.df   <- split(sf.df[["STOP WITH SEARCH OR FRISK"]], sf.df[["STOP WITH SEARCH OR FRISK"]]$RACE)

names(sf.race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = sf.race.df[[df]],
                color =  "red",
                weight = 1,
                radius = 6,
                fill = FALSE,
               group = df
       )
    })
    
               
l %>%
  addLayersControl(
    baseGroups =  names(race.beats),
    overlayGroups =  c(names(race.df)),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  htmlwidgets::onRender("
    function(el, x) {
      this.on('baselayerchange', function(e) {
        e.layer.bringToBack();
      })
    }") %>%
    addLegend("bottomleft", pal = racepal, values = names(race.df),
    title = "Race",
    opacity = 1
  )


```

### 2016-2017
``` {r }

l <-NULL

beats_data <- 
beats  %>% 
  mutate(`Percent White` = round(whitepopE/totalpopE*100,2),
         `Percent Black` = round(blackpopE/totalpopE*100,2)
        ) 

colorswhite <- colorRampPalette(brewer.pal(9, "Greens"))(9)[2:6]
whitepal <- colorBin(palette = colorswhite, domain = c(0,100), bins = 5)

colorsblack<- colorRampPalette(brewer.pal(9, "Purples"))(9)[2:6]
blackpal <- colorBin(palette = colorsblack, domain = c(0,100), bins = 5)

race.beats <- list(
      `Data Off` = beats_data %>% mutate(color = 0, df = "Data Off"),
     `Percent White` = beats_data %>% mutate(color = `Percent White`, df = "Percent White"),
     `Percent Black` = beats_data %>% mutate(color = `Percent Black`, df = "Percent Black")
     )

beatscolorfunction <- function(listname, color){
case_when(
     listname == names(race.beats)[2] ~   whitepal(color),
     listname == names(race.beats)[3] ~   blackpal(color),
     TRUE ~ "DCF0EF"
    )
}

beatsopacityfunction <- function(listname){
case_when(
     listname == names(race.beats)[2] ~   .5,
     listname == names(race.beats)[3] ~  .5,
     TRUE ~ 0
    )
}


l <- leaflet() %>%
  addProviderTiles("Stamen.Toner",
                   options = providerTileOptions(minZoom = 13))   %>%
  addMapPane("polygons", zIndex = 410) %>%
  addMapPane("circlemarkers", zIndex = 420) 

names(race.beats) %>%
   purrr::walk( function(df) {
    l <<- l %>%
           addPolygons(
              data = race.beats[[df]],
              weight = 3,
              fillOpacity = ~beatsopacityfunction(df),
              color = ~beatscolorfunction(df, color),
              group = df   ,
             smoothFactor = 0.5,
             label = ~htmlEscape(NAME)

              )
    })

## Add Race Dot Colors ## 

sflocationsmap <- 
  sflocations %>%
  mutate(RACE = ifelse(RACE == "W", "White", "Black")) %>%
  filter(Year > 2015) %>% ##################################################### YEAR 
   mutate(labels =  paste0( '<p> Race:', RACE, '<p></p>', 
         SFTYPE, '</p><p> Offense:', 
          OFFENSE, '</p>' ) 
)
  
race.df <- split(sflocationsmap, sflocationsmap$RACE)
race.colors <- data.frame()

mycolors <- c("#6969B3", "#00AF98")
racelevels <- names(race.df)
racepal <- colorFactor(palette = mycolors,
                   domain = racelevels)

names(race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = race.df[[df]],
                fillColor = ~racepal(df),
                weight = 0,
                radius = 2.5,
               fillOpacity = 1,
               group = df
       )
    }) 
  
sf.df <- split(sflocationsmap, sflocationsmap$SFTYPE)
sf.race.df   <- split(sf.df[["STOP WITH SEARCH OR FRISK"]], sf.df[["STOP WITH SEARCH OR FRISK"]]$RACE)

names(sf.race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = sf.race.df[[df]],
                color =  "red",
                weight = 1,
                radius = 6,
                fill = FALSE,
               group = df
       )
    })
    
               
l %>%
  addLayersControl(
    baseGroups =  names(race.beats),
    overlayGroups =  c(names(race.df)),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  htmlwidgets::onRender("
    function(el, x) {
      this.on('baselayerchange', function(e) {
        e.layer.bringToBack();
      })
    }")  %>%
    addLegend("bottomleft", pal = racepal, values = names(race.df),
    title = "Race",
    opacity = 1
  )


```

Row 
----------------------------------------------
### Exclusive Spaces

This is where I think we could tie in some narrative that you are collecting, Jordy, to analyze some specific spaces that may have more fraught histories. I gave an example with the Mall. 


Row {data-height=600}
----------------------------------------------

### Downtown {data-width=600}
``` {r}
l <- NULL

beats_data <- 
beats  %>% 
  mutate(`Percent White` = round(whitepopE/totalpopE*100,2),
         `Percent Black` = round(blackpopE/totalpopE*100,2)
        ) 

beatsopacityfunction <- function(BEAT_NO){
case_when(
     BEAT_NO == "01"  ~   0,
     TRUE ~ .9
    )
}

l <- leaflet(options = leafletOptions(zoomControl = FALSE)) %>%
  addProviderTiles("Stamen.Toner",
                   options = providerTileOptions(minZoom = 15, maxZoom = 17))   %>%
         setView( lng = -78.4795, lat = 38.0305, zoom = 16) %>%

  addMapPane("polygons", zIndex = 410) %>%
  addMapPane("circlemarkers", zIndex = 420) %>%
    # setMaxBounds( lng1 = -87.94011
    #              , lat1 = 41.64454
    #              , lng2 = -87.52414
    #              , lat2 = 42.02304 ) %>%
           addPolygons(
              data = beats_data,
              weight = 3,
              fillOpacity = ~beatsopacityfunction(BEAT_NO),
              color = "grey",
               smoothFactor = 0.5,

              )

## Add Race Dot Colors ## 
sflocationsmap <- 
  sflocations %>%
  mutate(RACE = ifelse(RACE == "W", "White", "Black")) %>%
  filter(BEAT_NO == 1) %>%
    mutate(labels =  paste0( '<p> Race:', RACE, '<p></p>', 
         SFTYPE, '</p><p> Offense:', 
          OFFENSE, '</p>' ) 
)
  
race.df <- split(sflocationsmap, sflocationsmap$RACE)
race.colors <- data.frame()

mycolors <- c("#6969B3", "#00AF98")
racelevels <- names(race.df)
racepal <- colorFactor(palette = mycolors,
                   domain = racelevels)

names(race.df) %>%
   purrr::walk(  function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = race.df[[df]],
                color = ~racepal(df),
                weight = 0,
                radius = 4,
               fillOpacity = 1,
               group = df)
    })
  
sf.df <- split(sflocationsmap, sflocationsmap$SFTYPE)
sf.race.df   <- split(sf.df[["STOP WITH SEARCH OR FRISK"]], sf.df[["STOP WITH SEARCH OR FRISK"]]$RACE)

names(sf.race.df) %>%
   purrr::walk( function(df) {
    l <<- l %>%
          addCircleMarkers(
                data = sf.race.df[[df]],
                color =  "red",
                weight = 1,
                radius = 7,
                fill = FALSE,
               group = df
       )
    }) 
               
l 

```


### This needs to be prettier

The Downtown Mall is a public space for free use by Charlottesville residents. 

* In the periods of 2012 -2014 and 2016-2017, 26 Black individuals were detained by police 
* 22 White individuals were detained in the same period. 
* 73% of Black individuals stopped (19 individuals) were also searched and frisked 
* 31% (7) of White individuals were also searched and frisked. 


What these analyses cannot account for is frequency of utilization of the space. Not many individuals live in this area, although 83% of those who do are white. Speaking with Charlottesville residents of color....




Offense {data-orientation=rows}
=====================================

Row {data-height = 200}
-----------------------------------------------------------------------

### Recorded Offense

We recoded the offense generating the detention as recorded in the data into the following categories: (1) Narcotics Investigations, (2) Suspicious Circumstances, (3) Disorderly conduct (including drunkeness), (4) Crimes on persons (e.g., assult, robbery, weapons), (5) Crimes on property (e.g., burglary, vandalism, trespassing), (6) Traffic-related events (e.g., traffic stops, violations, accidents), and (7) everything else (e.g., assistance, unidentified).

Row {.tabset}
-----------------------------------------------------------------------

### Detention by Recorded Offense

```{r}
sf_race <- sf_race %>%
  mutate(offense7 = case_when(
    str_detect(offense, "Assault|Robbery|PURSE|Shots|Weapon") ~ "Person Crime",
    str_detect(offense, "Burglary|Larceny|Trespass|VANDAL") ~ "Property Crime",
    str_detect(offense, "Narcotic") ~ "Narcotics Related",
    str_detect(offense, "Traffic") ~ "Traffic Related",
    str_detect(offense, "Disorder|Drunk|Liquor|INDECENT|DIP") ~ "Public Disorder",
    str_detect(offense, "Suspicious|Supsicious") ~ "Suspicious Circumstance",
    TRUE ~ "Other"
  ))

sf_race <- sf_race %>%
  mutate(offense7 = factor(offense7),
         offense7 = fct_infreq(offense7))

# for annotation
tots <- sf_race %>% group_by(offense7) %>% summarize(tots = n())
racetots <- sf_race %>% group_by(offense7, race) %>% summarize(racetot = n())
racetots <- racetots %>% left_join(tots)
racetots <- racetots %>% mutate(percent = round((racetot/tots)*100,0),
                                percent_lab = ifelse(tots < 40 & racetot < 15 ,"",  paste0(percent, "%")),
                                race = fct_relevel(race, "White"),
                                racetot = ifelse(race == "White", racetot*-1, racetot),
                                lab_pos = racetot/2)

ggplot(racetots, aes(x = offense7, fill = race, y = racetot)) +
  geom_bar(stat = "identity") + labs(fill = "Race") +
  scale_fill_manual(values = pal2) +
  geom_text(data = racetots, aes(x = offense7, y = lab_pos, label = percent_lab), size = 3) +
  coord_flip() +
  labs(y = "# Detentions", x = "Offense") +
  scale_y_continuous(labels = function(x){abs(x)}, limits = c(-120, 120))
```


### By Time Period

```{r}
# for annotation
tots <- sf_race %>% group_by(offense7, period) %>% summarize(tots = n())
racetots <- sf_race %>% group_by(offense7, race, period) %>% summarize(racetot = n())
racetots <- racetots %>% left_join(tots)
racetots <- racetots %>% ungroup() %>% mutate(percent = round((racetot/tots)*100,0),
                                percent_lab = ifelse(tots < 40 & racetot < 10 ,"",  paste0(percent, "%")),
                                race = fct_relevel(race, "White"),
                                racetot = ifelse(race == "White", racetot*-1, racetot),
                                lab_pos = racetot/2)

ggplot(racetots, aes(x = offense7, fill = race, y = racetot)) +
  geom_bar(stat = "identity") + labs(fill = "Race") +
  scale_fill_manual(values = pal2) +
  geom_text(data = racetots, aes(x = offense7, y = lab_pos, label = percent_lab), size = 3) +
  coord_flip() +
  labs(y = "# Detentions", x = "Offense") +
  scale_y_continuous(labels = function(x){abs(x)}, limits = c(-95, 95)) +
  facet_wrap(~period, nrow = 2) 
```


### By Stop and Frisk

```{r}
tots <- sf_race %>% group_by(offense7, type2) %>% summarize(tots = n())
racetots <- sf_race %>% group_by(offense7, race, type2) %>% summarize(racetot = n())
racetots <- racetots %>% left_join(tots)
racetots <- racetots %>% ungroup() %>% mutate(percent = round((racetot/tots)*100,0),
                                percent_lab = ifelse(tots < 40 & racetot < 10 ,"",  paste0(percent, "%")),
                                race = fct_relevel(race, "White"),
                                racetot = ifelse(race == "White", racetot*-1, racetot),
                                lab_pos = racetot/2)

ggplot(racetots, aes(x = offense7, fill = race, y = racetot)) +
  geom_bar(stat = "identity") + labs(fill = "Race") +
  scale_fill_manual(values = pal2) +
  geom_text(data = racetots, aes(x = offense7, y = lab_pos, label = percent_lab), size = 3) +
  coord_flip() +
  labs(y = "# Detentions", x = "Offense") +
  scale_y_continuous(labels = function(x){abs(x)}, limits = c(-120, 120), breaks = seq(-120,120,20)) +
  facet_wrap(~type2, nrow = 2) 
```
